S. Bikulcius Thesis: Analysis

### 2024-07-24 S. Bikulcius Thesis/analysis_report.Rmd

cog |>
  dplyr::select(subject, ends_with("_c")) |>
  dplyr::rename("Working Memory" = list_sort_c,
                "Inhibitory Control" = flanker_c,
                "Cognitive Flexibility" = card_sort_c,
                "Processing Speed" = pattern_c) |>
  tidyr::pivot_longer(cols = 'Working Memory':'Processing Speed',
                      names_to = "cog_measure",
                      values_to = "score") |>
  ggplot() +
  aes(x = score,
      y = cog_measure,
      color = cog_measure,
      fill = cog_measure) +
  geom_density_ridges(jittered_points = T,
                      position = position_points_jitter(width = 0.05, height = 0),
                      point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.5) +
  labs(x = "Score", y = "", color = "Cognitive Measure", fill = "Cognitive Measure") +
  scale_color_manual(values = c(my_pal[3],my_pal[4], my_pal[5], my_pal[6])) +
  scale_fill_manual(values = c(my_pal[3],my_pal[4], my_pal[5], my_pal[6])) +
  theme_classic()

>>>>

cog |>
  dplyr::select(subject, ends_with("_c")) |>
  dplyr::rename("Working Memory" = list_sort_c,
                "Inhibitory Control" = flanker_c,
                "Cognitive Flexibility" = card_sort_c,
                "Processing Speed" = pattern_c) |>
  tidyr::pivot_longer(cols = 'Working Memory':'Processing Speed',
                      names_to = "cog_measure",
                      values_to = "score") |>
  ggplot() +
  aes(x = score,
      y = cog_measure,
      color = cog_measure,
      fill = cog_measure) +
  geom_density_ridges(jittered_points = T,
                      position = position_points_jitter(width = 0.05, height = 0),
                      point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.5) +
  labs(x = "Score", y = "", color = "Cognitive Measure", fill = "Cognitive Measure") +
  scale_color_manual(values = c(my_pal[3],my_pal[4], my_pal[5], my_pal[6])) +
  scale_fill_manual(values = c(my_pal[3],my_pal[4], my_pal[5], my_pal[6])) +
  theme_classic() +
  theme(legend.position = "none")

ggsave("Figures/cog_distribution.png", plot = last_plot())
